---
title: "Gross Analysis"
author: "He YOU"
date: "November 18, 2017"
output: pdf_document
---

```{r}
library(stringr)
library(ggplot2)
library(MASS)
library(dplyr)

# prepared the matrixs needed

genres = read.csv("data/genre.csv")
movie = read.csv("data/movie_metadata_filtered.csv")
keywords = read.csv("data/keywords.csv")
actors = read.csv("data/actors.csv")
directors = read.csv("data/directors.csv")

genres_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(genres)[1])
colnames(genres_matrix)= genres$genres



for(i in 1:dim(genres)[1]){
genres_matrix[,i] =genres_matrix[,i] + 
  str_detect(movie$genres,pattern = as.character(genres[i,1]))
}

keywords_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(keywords)[1])
colnames(keywords_matrix)= keywords$plot_keywords

for(i in 1:dim(keywords)[1]){
keywords_matrix[,i] =keywords_matrix[,i] + 
  str_detect(movie$plot_keywords,pattern = as.character(keywords[i,1]))
}

actors_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(actors)[1])
colnames(actors_matrix)= actors$actor

for(i in 1:dim(actors)[1]){
actors_matrix[,i] =actors_matrix[,i] + 
  str_detect(movie$actor_1_name,pattern = as.character(actors[i,1]))  +
  str_detect(movie$actor_2_name,pattern = as.character(actors[i,1])) +
  str_detect(movie$actor_3_name,pattern = as.character(actors[i,1])) 
}

actors_matrix[actors_matrix > 0] = 1

directors_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(directors)[1])
colnames(directors_matrix)= directors$director_name

for(i in 1:dim(directors)[1]){
  directors_matrix[,i] =directors_matrix[,i] + 
  str_detect(movie$director_name,pattern =  as.character(directors[i,1]))
}

rm(actors,genres,keywords,directors,i)
```


```{r}
#get a new datafarme contains movie & genre information

movie_genres = data.frame(movie,genres_matrix)

```

# Check all the variables
```{r}
names(movie)
```

The numerical variables include: num_critic_for_reviews, duration,director_facebook_likes, actor_3_facebook_likes, actor_1_facebook_likes, num_voted_users, cast_total_facebook_like, facenumber_in_poster, budget, actor_2_facebook_likes, imdb_score, aspect_ratio, movie_facebook_likes

The categorical variables include: director_name, actor_1_name, actor_2_name, actor_3_name, genres and plot_keywords.

## Analysis into numerical variables

# gross in million
Firstly, we calculate gross and budget in million, so that budget will not be over-valued in this model.
```{r}
library(dplyr)
movie1=movie %>%
  mutate(budget=budget/1000000)%>%
  mutate(gross=gross/1000000)
```

# Select numerical variables to be analysed
We assumed that gross has relationship with both production and marketing process, thus gross is probably affected by factors including budget,duration and popularity of director and cast (which is reflected by Facebook likes). Additionally, gross is also related to marketing

```{r}
data=dplyr::select(movie1,gross,budget,duration,title_year,director_facebook_likes, imdb_score, actor_1_facebook_likes, actor_2_facebook_likes,actor_3_facebook_likes, cast_total_facebook_likes, movie_facebook_likes, num_voted_users, num_critic_for_reviews, facenumber_in_poster)

set.seed(1)
train_n=sample(dim(data)[1],0.75*dim(data)[1])
train_data=data[train_n,]
test_data=data[-train_n,]
```

# Create correlation matrix
Firstly, 
```{r}
library(corrplot)
cor(train_data,use="na.or.complete")
corrplot(cor(train_data,use="na.or.complete"))
```
From the graph we could see that there is strong positive relationship between gross and budget. And number of critic for reviews and number of voted users on IMDb also show apparent positive relationship with gross. Other factors also have positive relationship with gross, though the relationship is weaker.

# Build a linear regression model
```{r}
M1=lm(gross~.,train_data)
summary(M1)
```

```{r}
M2=lm(gross~.-facenumber_in_poster,train_data)
summary(M2)
```

```{r}
M3=lm(gross~.-facenumber_in_poster-movie_facebook_likes,train_data)
summary(M3)
```

```{r}
M4=lm(gross~.-facenumber_in_poster-movie_facebook_likes-imdb_score,train_data)
summary(M4)
```

```{r}
M5=lm(gross~.-facenumber_in_poster-movie_facebook_likes-imdb_score-title_year,train_data)
summary(M5)
```


```{r}
M6=lm(gross~.-facenumber_in_poster-movie_facebook_likes-imdb_score-title_year-num_critic_for_reviews,train_data)
summary(M6)
```

```{r}
M7=lm(gross~.-facenumber_in_poster-movie_facebook_likes-imdb_score-title_year-num_critic_for_reviews-duration,train_data)
summary(M7)
```
From this model, budget has a strong positive relationship with gross

## Analysis into categorical variables

# Identify top 8 genres leading to high gross
Build Ridge model and Lasso model to help us identify genres that have relationship with gross.

```{r}
library(glmnet)
gross.genres=data.frame(movie$gross,genres_matrix)
gross.genres=na.omit(gross.genres)
x=model.matrix(movie.gross~.,gross.genres)[,-1]
y=gross.genres$movie.gross
y=scale(y)
set.seed(1)
train=sample(dim(x)[1],0.75*dim(x)[1])
```

1.Ridge model
```{r}
ridge.mod=glmnet(x[train,],y[train],alpha=0)
set.seed(1)
ridge.cv.out=cv.glmnet(x[train,],y[train],alpha=0)
ridge.best.lam=ridge.cv.out$lambda.min
ridge.pre=predict(ridge.mod,s=ridge.best.lam,newx = x[-train,])
MSE.ridge=mean((ridge.pre-y[-train])^2)
MSE.ridge
```

2.Lasso model
```{r}
lasso.mod=glmnet(x[train,],y[train],alpha = 1)
set.seed(1)
lasso.cv.out=cv.glmnet(x[train,],y[train],alpha=1)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lasso.mod,s=lasso.best.lam,newx = x[-train,])
MSE.lasso=mean((lasso.pre-y[-train])^2)
MSE.lasso
```
```{r}
dim(genres_matrix)[2]
```

Since MSE for ridge model and lasso model are nearly the same, we use lasso model to generate coefficients, so that we could get less number of coefficients.

```{r}
genres.ridge.coef=predict(ridge.mod,type="coefficients",s=ridge.best.lam)[1:24,]
genres.co=data.frame(genres.ridge.coef)
genres.co=data.frame(rownames(genres.co),genres.co)[-1,]

ordered.desc.genres=genres.co %>%
  arrange(desc(genres.ridge.coef))
ordered.desc.genres

ordered.asc.genres=genres.co %>%
  arrange(genres.ridge.coef)
ordered.asc.genres

colnames(genres.co)=c("genres","gross_coef")
```

# Identify top keywords leading to high gross
```{r}
gross.keywords=data.frame(movie$gross,keywords_matrix)
gross.keywords=na.omit(gross.keywords)
x=model.matrix(movie.gross~.,gross.keywords)[,-1]
y=gross.keywords$movie.gross
y=scale(y)
set.seed(1)
train=sample(dim(x)[1],0.75*dim(x)[1])
```

1.Ridge model
```{r}
ridge.mod=glmnet(x[train,],y[train],alpha = 0)
set.seed(1)
ridge.cv.out=cv.glmnet(x[train,],y[train],alpha = 0)
ridge.best.lambda=ridge.cv.out$lambda.min
ridge.pre=predict(ridge.mod,s=ridge.best.lam,newx = x[-train,])
MSE.ridge=mean((ridge.pre-y[-train])^2)
MSE.ridge
```


2.Lasso model
```{r}
lasso.mod=glmnet(x[train,],y[train],alpha=1)
set.seed(1)
lasso.cv.out=cv.glmnet(x[train,],y[train],alpha=1)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lasso.mod,s=lasso.best.lam,newx = x[-train,])
MSE.lasso=mean((lasso.pre-y[-train])^2)
MSE.lasso
```


```{r}
dim(keywords_matrix)[2]
```

```{r}
keywords.ridge.coef=predict(ridge.mod,type="coefficients",s=ridge.best.lam)[1:5254,]
keywords.co=data.frame(keywords.ridge.coef)
keywords.co=data.frame(rownames(keywords.co),keywords.co)[-1,]


ordered.desc.keywords=keywords.co %>%
  arrange(desc(keywords.ridge.coef))
ordered.desc.keywords

ordered.asc.keywords=keywords.co %>%
  arrange(keywords.ridge.coef)
ordered.asc.keywords

colnames(keywords.co)=c("keywords","gross_coef")
```

# Identify directors leading to high gross
```{r}
gross.directors=data.frame(movie$gross,directors_matrix)
gross.directors=na.omit(gross.directors)
x=model.matrix(movie.gross~.,gross.directors)[,-1]
y=gross.directors$movie.gross
y=scale(y)
set.seed(1)
train=sample(dim(x)[1],0.75*dim(x)[1])
```
Use Ridge model and Lasso model to analyse relationship between directors and gross.

1.Ridge model
```{r}
ridge.mod=glmnet(x[train,],y[train],alpha = 0)
set.seed(1)
ridge.cv.out=cv.glmnet(x[train,],y[train],alpha = 0)
ridge.best.lambda=ridge.cv.out$lambda.min
ridge.pre=predict(ridge.mod,s=ridge.best.lam,newx = x[-train,])
MSE.ridge=mean((ridge.pre-y[-train])^2)
MSE.ridge
```

2.Lasso model
```{r}
lasso.mod=glmnet(x[train,],y[train],alpha=1)
set.seed(1)
lasso.cv.out=cv.glmnet(x[train,],y[train],alpha=1)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lasso.mod,s=lasso.best.lam,newx = x[-train,])
MSE.lasso=mean((lasso.pre-y[-train])^2)
MSE.lasso
```


```{r}
dim(directors_matrix)[2]
```


We use Ridge model to generate coefficients.
```{r}
directors.ridge.coef=predict(ridge.mod,type="coefficients",s=ridge.best.lam)[1:1466,]
directors.co=data.frame(directors.ridge.coef)
directors.co=data.frame(rownames(directors.co),directors.co)[-1,]


ordered.desc.directors=directors.co %>%
  arrange(desc(directors.ridge.coef))
ordered.desc.directors

ordered.asc.directors=directors.co %>%
  arrange(directors.ridge.coef)
ordered.asc.directors

colnames(directors.co)=c("directors","gross_coef")
```

# Identify actors and their relationship to high gross
```{r}
gross.actors=data.frame(movie$gross,actors_matrix)
gross.actors=na.omit(gross.actors)
x=model.matrix(movie.gross~.,gross.actors)[,-1]
y=gross.actors$movie.gross
y=scale(y)
set.seed(1)
train=sample(dim(x)[1],0.75*dim(x)[1])
```
Use Ridge model and Lasso model to analyse relationship between actors and gross.

1.Ridge model
```{r}
ridge.mod=glmnet(x[train,],y[train],alpha = 0)
set.seed(1)
ridge.cv.out=cv.glmnet(x[train,],y[train],alpha = 0)
ridge.best.lambda=ridge.cv.out$lambda.min
ridge.pre=predict(ridge.mod,s=ridge.best.lam,newx = x[-train,])
MSE.ridge=mean((ridge.pre-y[-train])^2)
MSE.ridge
```


```{r}
dim(actors_matrix)[2]
```

2.Lasso model
```{r}
lasso.mod=glmnet(x[train,],y[train],alpha=1)
set.seed(1)
lasso.cv.out=cv.glmnet(x[train,],y[train],alpha=1)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lasso.mod,s=lasso.best.lam,newx = x[-train,])
MSE.lasso=mean((lasso.pre-y[-train])^2)
MSE.lasso
```


```{r}
actors.ridge.coef=predict(ridge.mod,type="coefficients",s=ridge.best.lam)[1:3550,]
actors.ridge.coef
actors.ridge.co=data.frame(actors.ridge.coef)
actors.ridge.co=data.frame(rownames(actors.ridge.co),actors.ridge.co)[-1,]

ordered.desc.actors=actors.ridge.co %>%
  arrange(desc(actors.ridge.coef))
ordered.desc.actors

ordered.asc.actors=actors.ridge.co %>%
  arrange(actors.ridge.coef)
ordered.asc.actors

colnames(actors.ridge.co)=c("actors","gross_coef")
```

```{r}
write.csv(actors.ridge.co,file = "actors_gross.csv")
write.csv(directors.co,file = "directors_gross.csv")
write.csv(genres.co,file = "genres_gross.csv")
write.csv(keywords.co,file = "keywords_gross.csv")
```

