---
title: "Gross Analysis"
author: "He YOU"
date: "November 18, 2017"
output: pdf_document
---

```{r}
library(stringr)
library(ggplot2)
library(MASS)
library(dplyr)

# prepared the matrixs needed

genres = read.csv("data/genre.csv")
movie = read.csv("data/movie_metadata_filtered.csv")
keywords = read.csv("data/keywords.csv")
actors = read.csv("data/actors.csv")
directors = read.csv("data/directors.csv")

genres_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(genres)[1])
colnames(genres_matrix)= genres$genres



for(i in 1:dim(genres)[1]){
genres_matrix[,i] =genres_matrix[,i] + 
  str_detect(movie$genres,pattern = as.character(genres[i,1]))
}

keywords_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(keywords)[1])
colnames(keywords_matrix)= keywords$plot_keywords

for(i in 1:dim(keywords)[1]){
keywords_matrix[,i] =keywords_matrix[,i] + 
  str_detect(movie$plot_keywords,pattern = as.character(keywords[i,1]))
}

actors_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(actors)[1])
colnames(actors_matrix)= actors$actor

for(i in 1:dim(actors)[1]){
actors_matrix[,i] =actors_matrix[,i] + 
  str_detect(movie$actor_1_name,pattern = as.character(actors[i,1]))  +
  str_detect(movie$actor_2_name,pattern = as.character(actors[i,1])) +
  str_detect(movie$actor_3_name,pattern = as.character(actors[i,1])) 
}

actors_matrix[actors_matrix > 0] = 1

directors_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(directors)[1])
colnames(directors_matrix)= directors$director_name

for(i in 1:dim(directors)[1]){
  directors_matrix[,i] =directors_matrix[,i] + 
  str_detect(movie$director_name,pattern =  as.character(directors[i,1]))
}

rm(actors,genres,keywords,directors,i)
```


```{r}
#get a new datafarme contains movie & genre information

movie_genres = data.frame(movie,genres_matrix)

```

# Check all the variables
```{r}
names(movie)
```

The numerical variables include: num_critic_for_reviews, duration,director_facebook_likes, actor_3_facebook_likes, actor_1_facebook_likes, num_voted_users, cast_total_facebook_like, facenumber_in_poster, budget, actor_2_facebook_likes, imdb_score, aspect_ratio, movie_facebook_likes

The categorical variables include: director_name, actor_1_name, actor_2_name, actor_3_name, genres and plot_keywords.

## Analysis into numerical variables

# Gross in million
Firstly, we calculate gross and budget in million, so that budget will not be over-valued in this model.
```{r}
library(dplyr)
movie1=movie %>%
  mutate(budget=budget/1000000)%>%
  mutate(gross=gross/1000000)
```

# Select numerical variables to be analysed
We assume that gross has relationship with both production and marketing process, thus gross is probably affected by factors including budget,duration and popularity of director and cast (which is reflected by Facebook likes). Additionally, gross is also affected by word-of-mouth marketing online, which could be reflected through IMDb score, number of voted users and number of critics for reviews. 

```{r}
data=dplyr::select(movie1,gross,budget,duration,title_year,director_facebook_likes,  actor_1_facebook_likes, actor_2_facebook_likes,actor_3_facebook_likes, cast_total_facebook_likes, movie_facebook_likes, num_voted_users, num_critic_for_reviews, facenumber_in_poster)

set.seed(1)
train_n=sample(dim(data)[1],0.75*dim(data)[1])
train_data=data[train_n,]
test_data=data[-train_n,]
```

# Create correlation matrix
Firstly, we create a correlation matrix to view relationship between gross and other factors.
```{r}
library(corrplot)
cor(train_data,use="na.or.complete")
corrplot(cor(train_data,use="na.or.complete"))
```
From the graph we could see that there is strong positive relationship between gross and budget. And number of critic for reviews and number of voted users on IMDb also show apparent positive relationship with gross. Other factors also have positive relationship with gross, though the relationship is weaker.

# Build a linear regression model
```{r}
M1=lm(gross~.,train_data)
summary(M1)
```

```{r}
M2=lm(gross~.-facenumber_in_poster,train_data)
summary(M2)
```

```{r}
M3=lm(gross~.-facenumber_in_poster-movie_facebook_likes,train_data)
summary(M3)
```

```{r}
M4=lm(gross~.-facenumber_in_poster-movie_facebook_likes-title_year,train_data)
summary(M4)
```

```{r}
M5=lm(gross~.-facenumber_in_poster-movie_facebook_likes-title_year-num_critic_for_reviews,train_data)
summary(M5)
```


From this model, budget has a strong positive relationship with gross

## Analysis into categorical variables
Then we further analyze categorical variables. We dig into genres, keywords, directors and actors respectively and find out coefficients of each object in order to identify top ones leading to high gross in each category.

# Identify relationship between genres and gross
Build Ridge model and Lasso model to help us identify genres that have relationship with gross.

```{r}
library(glmnet)
gross.genres=data.frame(movie$gross,genres_matrix)
gross.genres=na.omit(gross.genres)
x=model.matrix(movie.gross~.,gross.genres)[,-1]
y=gross.genres$movie.gross
y=scale(y)
set.seed(1)
train=sample(dim(x)[1],0.75*dim(x)[1])
```

1.Ridge model
```{r}
ridge.mod=glmnet(x[train,],y[train],alpha=0)
set.seed(1)
ridge.cv.out=cv.glmnet(x[train,],y[train],alpha=0)
ridge.best.lam=ridge.cv.out$lambda.min
ridge.pre=predict(ridge.mod,s=ridge.best.lam,newx = x[-train,])
MSE.ridge=mean((ridge.pre-y[-train])^2)
MSE.ridge
```

2.Lasso model
```{r}
lasso.mod=glmnet(x[train,],y[train],alpha = 1)
set.seed(1)
lasso.cv.out=cv.glmnet(x[train,],y[train],alpha=1)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lasso.mod,s=lasso.best.lam,newx = x[-train,])
MSE.lasso=mean((lasso.pre-y[-train])^2)
MSE.lasso
```
```{r}
dim(genres_matrix)[2]
```
Since MSE for ridge model and lasso model are nearly the same, and we would like to identify first genres and last ones leading to high gross. Thus, we use Ridge model to generate coefficients to keep more genres in outcomes.

```{r}
genres.ridge.coef=predict(ridge.mod,type="coefficients",s=ridge.best.lam)[1:24,]
genres.co=data.frame(genres.ridge.coef)[-1,]
genres.co=data.frame(colnames(genres_matrix),genres.co)

ordered.desc.genres=genres.co %>%
  arrange(desc(genres.co))
ordered.desc.genres

ordered.asc.genres=genres.co %>%
  arrange(genres.co)
ordered.asc.genres

colnames(genres.co)=c("genres","gross_coef")
```

# Identify relationship between keywords and gross
```{r}
gross.keywords=data.frame(movie$gross,keywords_matrix)
gross.keywords=na.omit(gross.keywords)
x=model.matrix(movie.gross~.,gross.keywords)[,-1]
y=gross.keywords$movie.gross
y=scale(y)
set.seed(1)
train=sample(dim(x)[1],0.75*dim(x)[1])
```

1.Ridge model
```{r}
ridge.mod=glmnet(x[train,],y[train],alpha = 0)
set.seed(1)
ridge.cv.out=cv.glmnet(x[train,],y[train],alpha = 0)
ridge.best.lambda=ridge.cv.out$lambda.min
ridge.pre=predict(ridge.mod,s=ridge.best.lam,newx = x[-train,])
MSE.ridge=mean((ridge.pre-y[-train])^2)
MSE.ridge
```


2.Lasso model
```{r}
lasso.mod=glmnet(x[train,],y[train],alpha=1)
set.seed(1)
lasso.cv.out=cv.glmnet(x[train,],y[train],alpha=1)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lasso.mod,s=lasso.best.lam,newx = x[-train,])
MSE.lasso=mean((lasso.pre-y[-train])^2)
MSE.lasso
```


```{r}
dim(keywords_matrix)[2]
```
For keywords analysis, we also use Ridge model to calculate coefficients.
```{r}
keywords.ridge.coef=predict(ridge.mod,type="coefficients",s=ridge.best.lam)[1:5254,]
keywords.co=data.frame(keywords.ridge.coef)[-1,]
keywords.co=data.frame(colnames(keywords_matrix),keywords.co)


ordered.desc.keywords=keywords.co %>%
  arrange(desc(keywords.co))
ordered.desc.keywords

ordered.asc.keywords=keywords.co %>%
  arrange(keywords.co)
ordered.asc.keywords

colnames(keywords.co)=c("keywords","gross_coef")
```

# Identify relationship between directors and gross
```{r}
gross.directors=data.frame(movie$gross,directors_matrix)
gross.directors=na.omit(gross.directors)
x=model.matrix(movie.gross~.,gross.directors)[,-1]
y=gross.directors$movie.gross
y=scale(y)
set.seed(1)
train=sample(dim(x)[1],0.75*dim(x)[1])
```
Use Ridge model and Lasso model to analyse relationship between directors and gross.

1.Ridge model
```{r}
ridge.mod=glmnet(x[train,],y[train],alpha = 0)
set.seed(1)
ridge.cv.out=cv.glmnet(x[train,],y[train],alpha = 0)
ridge.best.lambda=ridge.cv.out$lambda.min
ridge.pre=predict(ridge.mod,s=ridge.best.lam,newx = x[-train,])
MSE.ridge=mean((ridge.pre-y[-train])^2)
MSE.ridge
```

2.Lasso model
```{r}
lasso.mod=glmnet(x[train,],y[train],alpha=1)
set.seed(1)
lasso.cv.out=cv.glmnet(x[train,],y[train],alpha=1)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lasso.mod,s=lasso.best.lam,newx = x[-train,])
MSE.lasso=mean((lasso.pre-y[-train])^2)
MSE.lasso
```


```{r}
dim(directors_matrix)[2]
```

We use Ridge model to generate coefficients.
```{r}
directors.ridge.coef=predict(ridge.mod,type="coefficients",s=ridge.best.lam)[1:1466,]
directors.co=data.frame(directors.ridge.coef)[-1,]
directors.co=data.frame(colnames(directors_matrix),directors.co)


ordered.desc.directors=directors.co %>%
  arrange(desc(directors.co))
ordered.desc.directors

ordered.asc.directors=directors.co %>%
  arrange(directors.co)
ordered.asc.directors

colnames(directors.co)=c("directors","gross_coef")
```

# Identify relationship between actors and gross
```{r}
gross.actors=data.frame(movie$gross,actors_matrix)
gross.actors=na.omit(gross.actors)
x=model.matrix(movie.gross~.,gross.actors)[,-1]
y=gross.actors$movie.gross
y=scale(y)
set.seed(1)
train=sample(dim(x)[1],0.75*dim(x)[1])
```
Use Ridge model and Lasso model to analyse relationship between actors and gross.

1.Ridge model
```{r}
ridge.mod=glmnet(x[train,],y[train],alpha = 0)
set.seed(1)
ridge.cv.out=cv.glmnet(x[train,],y[train],alpha = 0)
ridge.best.lambda=ridge.cv.out$lambda.min
ridge.pre=predict(ridge.mod,s=ridge.best.lam,newx = x[-train,])
MSE.ridge=mean((ridge.pre-y[-train])^2)
MSE.ridge
```


```{r}
dim(actors_matrix)[2]
```

2.Lasso model
```{r}
lasso.mod=glmnet(x[train,],y[train],alpha=1)
set.seed(1)
lasso.cv.out=cv.glmnet(x[train,],y[train],alpha=1)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lasso.mod,s=lasso.best.lam,newx = x[-train,])
MSE.lasso=mean((lasso.pre-y[-train])^2)
MSE.lasso
```

We use Ridge model to generate coefficients.
```{r}
actors.ridge.coef=predict(ridge.mod,type="coefficients",s=ridge.best.lam)[1:3550,]
actors.ridge.co=data.frame(actors.ridge.coef)[-1,]
actors.ridge.co=data.frame(colnames(actors_matrix),actors.ridge.co)

ordered.desc.actors=actors.ridge.co %>%
  arrange(desc(actors.ridge.co))
ordered.desc.actors

ordered.asc.actors=actors.ridge.co %>%
  arrange(actors.ridge.co)
ordered.asc.actors

colnames(actors.ridge.co)=c("actors","gross_coef")
```

Finally, generate related csv files for further analysis.
```{r}
write.csv(actors.ridge.co,file = "actors_gross.csv")
write.csv(directors.co,file = "directors_gross.csv")
write.csv(genres.co,file = "genres_gross.csv")
write.csv(keywords.co,file = "keywords_gross.csv")
```

