%>% %>% %>% ---
title: "score"
author: "Zhuqoun Sheng"
date: "November 18, 2017"
output: pdf_document
---

```{r}
library(stringr)
library(ggplot2)
library(dplyr)

# prepared the matrixs needed

genres = read.csv("data/genre.csv")
movie = read.csv("data/movie_metadata_filtered.csv")
keywords = read.csv("data/keywords.csv")
actors = read.csv("data/actors.csv")
directors = read.csv("data/directors.csv")

genres_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(genres)[1])
colnames(genres_matrix)= genres$genres



for(i in 1:dim(genres)[1]){
genres_matrix[,i] =genres_matrix[,i] + 
  str_detect(movie$genres,pattern = as.character(genres[i,1]))
}

keywords_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(keywords)[1])
colnames(keywords_matrix)= keywords$plot_keywords

for(i in 1:dim(keywords)[1]){
keywords_matrix[,i] =keywords_matrix[,i] + 
  str_detect(movie$plot_keywords,pattern = as.character(keywords[i,1]))
}

actors_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(actors)[1])
colnames(actors_matrix)= actors$actor

for(i in 1:dim(actors)[1]){
actors_matrix[,i] =actors_matrix[,i] + 
  str_detect(movie$actor_1_name,pattern = as.character(actors[i,1]))  +
  str_detect(movie$actor_2_name,pattern = as.character(actors[i,1])) +
  str_detect(movie$actor_3_name,pattern = as.character(actors[i,1])) 
}

actors_matrix[actors_matrix > 0] = 1

directors_matrix = matrix(0,
                    nrow=dim(movie)[1],
                    ncol=dim(directors)[1])
colnames(directors_matrix)= directors$director_name

for(i in 1:dim(directors)[1]){
  directors_matrix[,i] =directors_matrix[,i] + 
  str_detect(movie$director_name,pattern =  as.character(directors[i,1]))
}

rm(actors,genres,keywords,directors,i)
```


```{r}
#mutate a new column represent the high score and low score
movie = mutate(movie,high_low = ifelse(imdb_score>7,1,0))

#get a new datafarme contains useful information
movie_useful = data.frame(movie$high_low,
                         movie$duration,
                         movie$actor_1_facebook_likes,
                         movie$actor_2_facebook_likes,
                         movie$actor_3_facebook_likes,
                         movie$num_voted_users,
                         movie$facenumber_in_poster,
                         movie$cast_total_facebook_likes,
                         movie$num_user_for_reviews,
                         movie$num_critic_for_reviews,
                         movie$budget,
                         movie$aspect_ratio,
                         movie$title_year)
movie_useful = na.omit(movie_useful)
```

```{r}
set.seed(1)
train_n =sample(1:dim(movie_useful)[1],                                                     dim(movie_useful)[1]*0.75)

train_data = movie_useful[train_n,]
test_data = movie_useful[-train_n,]

glm=glm(movie.high_low~.,
       data=train_data,
       family="binomial")
summary(glm)
```

```{r}
glm=glm(movie.high_low~.-movie.actor_3_facebook_likes,
       data=train_data,
       family="binomial")
summary(glm)
```
```{r}
glm=glm(movie.high_low~.-movie.actor_3_facebook_likes-movie.actor_2_facebook_likes,
       data=train_data,
       family="binomial")
summary(glm)
```
```{r}
glm=glm(movie.high_low~.-movie.actor_3_facebook_likes-movie.actor_2_facebook_likes-movie.cast_total_facebook_likes,
       data=train_data,
       family="binomial")
summary(glm)
```
```{r}
glm=glm(movie.high_low~.-movie.actor_3_facebook_likes-movie.actor_2_facebook_likes-movie.cast_total_facebook_likes-movie.actor_1_facebook_likes,
       data=train_data,
       family="binomial")
summary(glm)
```

Step by step, we elimated some variables' effect, include actor's facebook likes and cast_total_facebook_likes. In another words, all the variables contains facebook's effect. The IMDB_Score have nothing relate to the facebook.

For the remined variables, the longer the movie, the higher the score which is a little superice, however, the year also is a significant variables means that recent years the movie get harder than before to get a score higher then 7.0.


```{r}
glm_predict=predict(glm,test_data,type="response") 
threshold_range = seq(0.01,0.4,by=0.01)
threshold = NULL
result = NULL
for(threshold in threshold_range){
glm.test.pre=rep("low",dim(test_data)[1])
glm.test.pre[glm_predict>=threshold]="high"
confusion_table=table(test_data$movie.high_low,glm.test.pre)
misclassification_error=(confusion_table[1,2]+confusion_table[2,1])/sum(confusion_table)
result = c(result,misclassification_error)
}
plot(threshold_range,result)
error_matrix = data.frame(threshold_range,result)
error_matrix = error_matrix %>% 
  arrange(result)
rm(error_matrix,glm,glm.test.pre,glm_predict,confusion_table,result,threshold,threshold_range,misclassification_error)
```
```{r}
library(MASS)
ldam = lda(movie.high_low~.-movie.title_year-movie.actor_3_facebook_likes-movie.actor_2_facebook_likes-movie.cast_total_facebook_likes-movie.actor_1_facebook_likes,data = train_data)
lda_pred = predict(ldam,test_data)
lda_pred_y = lda_pred$class
testing_y = test_data$movie.high_low
table(testing_y,lda_pred_y)
mean(testing_y!=lda_pred_y)
rm(lda_pred,lda_pred_y,ldam)
```
```{r}
qdam = qda(movie.high_low~.-movie.actor_3_facebook_likes-movie.actor_2_facebook_likes-movie.cast_total_facebook_likes-movie.actor_1_facebook_likes-movie.title_year,data = train_data)
qda_pred = predict(qdam,test_data)
qda_pred_y = qda_pred$class
testing_y = test_data$movie.high_low
table(testing_y,qda_pred_y)
mean(testing_y!=qda_pred_y)
rm(qda_pred,qda_pred_y,qdam)
```

```{r, warning= FALSE}
library(class)
train_high_low = train_data$movie.high_low
test_high_low = test_data$movie.high_low
test_data_scaled = scale(test_data)
train_data_scaled = scale(train_data)
k_range = seq(1,50,by=1)
k = NULL
train_errors = NULL
test_errors = NULL
for(kk in k_range){
knn_pred =knn(train_data_scaled,test_data_scaled,train_high_low,k=kk)
misclassification_error = mean(test_high_low != knn_pred)
test_errors = c(test_errors,misclassification_error)

misclassification_error = mean(train_high_low != knn_pred)
train_errors = c(train_errors,misclassification_error)
}
plot(k_range,test_errors)
plot(k_range,train_errors)

error_matrix = data.frame(k_range,test_errors,train_errors)
error_matrix = error_matrix %>% 
  mutate(sumerrors = test_errors + train_errors) %>% 
  arrange(sumerrors)
rm(error_matrix,test_data_scaled,train_data_scaled,k,k_range,kk,knn_pred,misclassification_error,test_high_low,test_errors,testing_y,train_errors,train_high_low)
```




In a conclusion, the lda model would be the best model to predict the high or low of the imdb score.Besides,the knn model and glm model have quite big misclassification error so we cannot use them.

To identify genres that have relationship with IMDB score,we used lasso and irdge model to identify.

```{r}
library(glmnet)

score_genres=data.frame(movie$movie_title,movie$high_low,genres_matrix)
score_genres=na.omit(score_genres)
x=model.matrix(movie.high_low~.,score_genres[,-1])[,-1]
y=score_genres$movie.high_low
set.seed(1)
train_n =sample(1:dim(score_genres)[1],                                                     dim(score_genres)[1]*0.75)
train_x = x[train_n,]
test_x = x[-train_n,]
train_y = y[train_n]
test_y = y[-train_n]
```

1.Ridge model
```{r}
ridgem=glmnet(train_x,train_y,alpha=0)
set.seed(1)
ridge.cv.out=cv.glmnet(train_x,train_y,alpha=0)
ridge.best.lam=ridge.cv.out$lambda.min
ridge.pre=predict(ridgem,s=ridge.best.lam,newx = x[-train_n,])
MSE.ridge=mean((ridge.pre-test_y)^2)
MSE.ridge
```

2.Lasso model
```{r}
lassom=glmnet(train_x,train_y,alpha=1)
set.seed(1)
lasso.cv.out=cv.glmnet(train_x,train_y,alpha=0)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lassom,s=lasso.best.lam,newx = test_x)
MSE.lasso=mean((lasso.pre-test_y)^2)
MSE.lasso
```

The results are pretty close,so we consider use lasso to identity the genres have the most important influence. 

```{r}
lasso.coef=predict(lassom,type="coefficients",s=lasso.best.lam)[1:dim(genres_matrix)[2]+1,]
lasso.coef=data.frame(colnames(genres_matrix),
                      data.frame(lasso.coef))
lasso.coef %>% 
  filter(lasso.coef!=0) %>% 
  arrange(desc(lasso.coef))
```
#actors


```{r}
score_actors=data.frame(movie$movie_title,movie$high_low,actors_matrix)
score_actors=na.omit(score_actors)
x=model.matrix(movie.high_low~.,score_actors[,-1])[,-1]
y=score_actors$movie.high_low
set.seed(1)
train_n =sample(1:dim(score_actors)[1],                                                     dim(score_actors)[1]*0.75)
train_x = x[train_n,]
test_x = x[-train_n,]
train_y = y[train_n]
test_y = y[-train_n]
```

1.Ridge model
```{r}
ridgem=glmnet(train_x,train_y,alpha=0)
set.seed(1)
ridge.cv.out=cv.glmnet(train_x,train_y,alpha=0)
ridge.best.lam=ridge.cv.out$lambda.min
ridge.pre=predict(ridgem,s=ridge.best.lam,newx = x[-train_n,])
MSE.ridge=mean((ridge.pre-test_y)^2)
MSE.ridge
```

2.Lasso model
```{r}
lassom=glmnet(train_x,train_y,alpha=1)
set.seed(1)
lasso.cv.out=cv.glmnet(train_x,train_y,alpha=0)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lassom,s=lasso.best.lam,newx = test_x)
MSE.lasso=mean((lasso.pre-test_y)^2)
MSE.lasso
```

The results are pretty close,so we consider use lasso to identity the genres have the most important influence. 

```{r}
lasso.coef=predict(lassom,type="coefficients",s=lasso.best.lam)[1:dim(actors_matrix)[2]+1,]
lasso.coef=data.frame(colnames(actors_matrix),
                      data.frame(lasso.coef))
actors.coef = lasso.coef %>% 
  filter(lasso.coef!=0) %>% 
  arrange(desc(lasso.coef))
```

However, none of the actors have significant influence on the imdb_score from lasso regression, we need to use ridge regression to identity.
```{r}
ridge.coef=predict(ridgem,type="coefficients",s=ridge.best.lam)[1:dim(actors_matrix)[2]+1,]
ridge.coef=data.frame(colnames(actors_matrix),
                      data.frame(ridge.coef))
actors.coef = ridge.coef %>% 
  filter(ridge.coef!=0) %>% 
  arrange(desc(ridge.coef))


colnames(actors.coef)=c("actors","score_coef")

actors.coef[1:10,1]
actors.coef[(dim(actors.coef)[1]-10):dim(actors.coef)[1],1]
```

#keywords


```{r}
score_keywords=data.frame(movie$movie_title,movie$high_low,keywords_matrix)
score_keywords=na.omit(score_keywords)
x=model.matrix(movie.high_low~.,score_keywords[,-1])[,-1]
y=score_keywords$movie.high_low
set.seed(1)
train_n =sample(1:dim(score_keywords)[1],                                                     dim(score_keywords)[1]*0.75)
train_x = x[train_n,]
test_x = x[-train_n,]
train_y = y[train_n]
test_y = y[-train_n]
```

1.Ridge model
```{r}
ridgem=glmnet(train_x,train_y,alpha=0)
set.seed(1)
ridge.cv.out=cv.glmnet(train_x,train_y,alpha=0)
ridge.best.lam=ridge.cv.out$lambda.min
ridge.pre=predict(ridgem,s=ridge.best.lam,newx = x[-train_n,])
MSE.ridge=mean((ridge.pre-test_y)^2)
MSE.ridge
```

2.Lasso model
```{r}
lassom=glmnet(train_x,train_y,alpha=1)
set.seed(1)
lasso.cv.out=cv.glmnet(train_x,train_y,alpha=0)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lassom,s=lasso.best.lam,newx = test_x)
MSE.lasso=mean((lasso.pre-test_y)^2)
MSE.lasso
```

The results are pretty close,so we consider use lasso to identity the keywords have the most important influence. 

```{r}
lasso.coef=predict(lassom,type="coefficients",s=lasso.best.lam)[1:dim(keywords_matrix)[2]+1,]
lasso.coef=data.frame(colnames(keywords_matrix),
                      data.frame(lasso.coef))
keywords.coef = lasso.coef %>% 
  filter(lasso.coef!=0) %>% 
  arrange(desc(lasso.coef))
```

There is no result

```{r}
ridge.coef=predict(ridgem,type="coefficients",s=ridge.best.lam)[1:dim(keywords_matrix)[2]+1,]
ridge.coef=data.frame(colnames(keywords_matrix),
                      data.frame(ridge.coef))
keywords.coef = ridge.coef %>% 
  filter(ridge.coef!=0) %>% 
  arrange(desc(ridge.coef))


colnames(keywords.coef)=c("keywords","score_coef")

keywords.coef[1:10,1]
keywords.coef[(dim(keywords.coef)[1]-10):dim(keywords.coef)[1],1]
```

#directors


```{r}
score_directors=data.frame(movie$movie_title,movie$high_low,directors_matrix)
score_directors=na.omit(score_directors)
x=model.matrix(movie.high_low~.,score_directors[,-1])[,-1]
y=score_directors$movie.high_low
set.seed(1)
train_n =sample(1:dim(score_directors)[1],                                                     dim(score_directors)[1]*0.75)
train_x = x[train_n,]
test_x = x[-train_n,]
train_y = y[train_n]
test_y = y[-train_n]
```

1.Ridge model
```{r}
ridgem=glmnet(train_x,train_y,alpha=0)
set.seed(1)
ridge.cv.out=cv.glmnet(train_x,train_y,alpha=0)
ridge.best.lam=ridge.cv.out$lambda.min
ridge.pre=predict(ridgem,s=ridge.best.lam,newx = x[-train_n,])
MSE.ridge=mean((ridge.pre-test_y)^2)
MSE.ridge
```

2.Lasso model
```{r}
lassom=glmnet(train_x,train_y,alpha=1)
set.seed(1)
lasso.cv.out=cv.glmnet(train_x,train_y,alpha=0)
lasso.best.lam=lasso.cv.out$lambda.min
lasso.pre=predict(lassom,s=lasso.best.lam,newx = test_x)
MSE.lasso=mean((lasso.pre-test_y)^2)
MSE.lasso
```

The results are pretty close,so we consider use lasso to identity the directors have the most important influence. 

```{r}
lasso.coef=predict(lassom,type="coefficients",s=lasso.best.lam)[1:dim(directors_matrix)[2]+1,]
lasso.coef=data.frame(colnames(directors_matrix),
                      data.frame(lasso.coef))
directors.coef = lasso.coef %>% 
  filter(lasso.coef!=0) %>% 
  arrange(desc(lasso.coef))
```

There is no result

```{r}
ridge.coef=predict(ridgem,type="coefficients",s=ridge.best.lam)[1:dim(directors_matrix)[2]+1,]
ridge.coef=data.frame(colnames(directors_matrix),
                      data.frame(ridge.coef))
directors.coef = ridge.coef %>% 
  filter(ridge.coef!=0) %>% 
  arrange(desc(ridge.coef))


colnames(directors.coef)=c("directors","score_coef")

directors.coef[1:10,1]
directors.coef[(dim(directors.coef)[1]-10):dim(directors.coef)[1],1]
```

